Scikit-learn: machine learning without learning the machinery

### 2014-11-06 article.tex
FIX: make example copy/pastable

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}

% Listing settings for Python
\lstset{language=python,
	extendedchars=true,
	xleftmargin = 0pt,
	%frame=single,
	%rulecolor=\color{lightgrey},
        aboveskip = 0.5ex,
        belowskip = 0.6ex,
	basicstyle=\small\sffamily,
	escapebegin={\color{green}},
        keywordstyle=\bfseries\color{blue!50!black},
	%identifierstyle=\sffamily\small,
	commentstyle=\color{green!40!black},
	stringstyle=\rmfamily\color{red!60!black},
	showstringspaces=false,
	tabsize=2,
	breaklines=true,
	%classoffset=1,
        morekeywords={{,},=,:}, %keywordstyle=\color{SkoleYellow},
	%classoffset=0,
	backgroundcolor=\color{green!10},
	fillcolor=\color{green!10},
}

>>>>

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{dblfloatfix}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[numbers,square]{natbib}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{url}
\usepackage{magazine-style}
\usepackage{textcomp}

\makeatletter
\newcommand*\verbfont{%
    \normalfont\ttfamily\hyphenchar\font\m@ne\@noligs}
\makeatother

% Listing settings for Python
\lstset{language=python,
	extendedchars=true,
    columns=fullflexible,
    upquote=true,
	xleftmargin = 0pt,
	%frame=single,
	%rulecolor=\color{lightgrey},
        aboveskip = 0.5ex,
        belowskip = 0.6ex,
	basicstyle=\verbfont,
	escapebegin={\color{green}},
        keywordstyle=\bfseries\color{blue!50!black},
	%identifierstyle=\sffamily\small,
	commentstyle=\color{green!40!black} \verbfont,
	stringstyle=\color{red!60!black} \verbfont,
	showstringspaces=false,
	tabsize=2,
	breaklines=true,
	%classoffset=1,
        morekeywords={{,},=,:}, %keywordstyle=\color{SkoleYellow},
	%classoffset=0,
	backgroundcolor=\color{green!10},
	fillcolor=\color{green!10},
}
